### 2020-07-02 Model Data Sheets and Code/Zaca MCF Mortality Model Results.Rmd
added methods/goals section

@@

@@

### Random Forest forced sample sizes

https://stats.stackexchange.com/questions/457451/how-r-randomforest-sampsize-works

tc_mortality 1 = type converted
tc_mortality 0 = "not_tc"

using for loop to generate several graphs so its easier to compare them
```{r}

>>>>

### Methods background

using forced sample sizes (see https://stats.stackexchange.com/questions/457451/how-r-randomforest-sampsize-works) because the distribution of observations in each mortality class is very uneven and results in a model that severely underpredicts observations in the mortality class with few observations. Bc of the small sample size, we will not be using training and test data (and bc RF basically creates its own train/test data).

Different RF trials:

  - Mixed confier forests
    + response variable: type conversion
    + response variable: 4 mortality classes (none, low, momderate, high)
    + response variable: 3 mortality classes (none/low, moderate, high)
    + response variable: 2 mortality classes (none/low/moderate, high)
    + response variable: rdnbr
  - Coulter pines 
    + response variable: rdnbr
  - mixed conifer forests and coulter pines combined
    + response variable: rdnbr

Note: manual classification of mortality and type conversion for the coulter pines was not done. Aint no one got time for that

The type conversion mortality classes-
tc_mortality 0 = "not_tc" (n=99)
tc_mortality 1 = type converted (n=>600)

### Goals/Questions

1. Can the mcf model distinguish between type conversion and the other mortality types? 
  - so far, no! so variable importance is not meaningful for that model

2. Which variables contribute to type conversion of MCFs?

3. How well does rdnbr compare to manual estimates of mortality?

4. How does using rdnbr and manually derived mortality compare as a response variable?

5. Which variables contribute to high/low mortality? high/low rdnbr?

5. Does conifer type contribute to different variable importances?

@@

ggplot(mcf, aes(x=ndvi, y=rdnbr_2007)) +
  geom_point()

ndvi_rdnbr_corr <- lm(rdnbr_2007~ndvi, data=mcf)
summary(ndvi_rdnbr_corr)

@@

### RF manual mortality: 4 classes (none, low, moderate, high)

Just using for loop to generate several graphs so its easier to compare them and make sure importance is stable
```{r}
